A single \dword{spmod} requires \num{3000} \dwords{femb}, \num{750} \dwords{wib}, and \num{50} \dwords{ptc}.  A total of \num{3300} \dwords{femb}, \num{900} \dwords{wib}, and \num{60} \dwords{ptc} will be built.

If the three-\dword{asic} \dword{femb} solution is chosen (the baseline option), then two \dword{asic} production contracts will be required, one for \dword{larasic} (\SI{180}{nm} \dword{cmos}) and one for the Cold \dword{adc} and \dword{coldata} (\SI{65}{nm} \dword{cmos}).  If the one-\dword{asic} \dword{femb} solution is chosen, only one \dword{asic} production contract will be required.

In either case, all \dwords{asic} will be packaged in plastic quad flat-pack (PQFP) or thin quad flat-pack (TQFP) surface mount packages.  No wafer probing will be done before the chips are packaged.  Rather, the wafers will be diced and all chips located more than $\sim$\SI{10}{mm} from the outside of the wafer will be selected for packaging.  The packaged parts will be tested by DUNE collaborators (see Section~\ref{sec:fdsp-tpc-elec-qc}) before being assembled onto printed circuit boards.

All printed circuit boards will be fabricated and tested by qualified vendors. Circuit boards will also be assembled by qualified vendors.  The completed boards will be acceptance tested by DUNE collaborators promptly after assembly.

All cable assemblies (including terminations) will be fabricated and tested by qualified vendors.  At least a fraction of the cable assemblies will be retested by DUNE collaborators promptly after purchase.

%This section appears incomplete in that it doesn't say anything about the warm electronics crates, or the cryostat \fdth boards, or the spool pieces (4-way crosses), or the inner support structures that connect to the bottom of the spool pieces (not sure what these are called) or the part that lives at the bottom of those inner support structures that controls the rate of (boil-off) argon gas purge out the spool pieces (& I'm not sure where that gas leaves the cryostat). 
