\subsection{Front-end Trigger Primitive Generation}
\label{sec:fd-daq-fetp}

In the nominal design, the \dword{bow} computers decompress the
\dword{cro} data stream and execute algorithms to search for per-channel
localized activity above some threshold based on a recent measure of
the noise. 
These \dwords{trigprimitive} are then sent out along with the original,
compressed \dword{cro} data to the \dword{fec} associated with the \dword{bow}.

Initial studies have shown some promise that this type of \dwords{trigprimitive} pipeline can be implemented on commodity CPUs and keep up
with the data. 
The studies made use of \dword{sp} signal and noise simulation but
given the relatively higher signal-to-noise ratio expected in the \dword{dpmod}
data, coupled with fewer total channels, these studies should
be applicable and even better performance may be expected. 
With that said, more realistic studies using \dword{dp}-specific
simuilations and with \dword{pddp} data are needed.

Most of the same technical triggering issues apply in the nominal and
the alternative design (generically diagrammed in
Figure~\ref{fig:daq-overview-alt}), as both call for deploying \dword{trigprimitive} pipelines on commodity CPUs. 
The main difference is that the \dwords{bow} hosts become trigger farm
hosts. 
They move from being upstream and inline of the data flow before the
\dword{fec} to being downstream and receiving the data after it has
been buffered. 
Their \dwords{trigcandidate} no longer have to be inserted into the
stream and stripped out by the \dword{fec} and instead are sent
directly to the \dword{mtl}. 
Additional study is required to understand the multiplicity of trigger
processing computers and how that might scale as one considers
different multiplicities of \dword{cro} \dword{utca} crates with respect to each
\dword{fec}.

In both designs, the \dword{lro} data is currently not considered for
triggering as the \dword{cro} triggering is expected to be more
efficient. However, using light information for triggering has not yet
been ruled out. 
Future studies may indicate additional benefit to including
\dword{lro} information in triggering and both the nominal and
alternative design can elastically accommodate this increased scope
although possibly at the cost of either more \dword{bow} or trigger
processor computers.
As described elsewhere, the \dword{lro} data flow is handled by
separate \dwords{daqfrag} from those that service the \dwords{cro}. 
Thus, if any \dwords{trigprimitive} and \dwords{trigcandidate} are to
be formed from \dword{lro} data they would come from these separate
fragments and be combined in the \dword{mtl} as peers of the
\dword{cro} and external candidates.

