\section{Integration Engineering}
\label{sec:fdsp-coord-integ-sysengr}
%				7 pages

The major aspects of detector integration focus on the mechanical and
electrical connections between each of the detector systems. This
includes verification that subassemblies and their interfaces are
correct (e.g., \dword{apa} and \single \dword{pds}). A second major area is in the support of
the %detector and its  
\dwords{detmodule} and their interfaces to the cryostat and cryogenics. A
third major area is in assuring that the \dwords{detmodule} %detector 
can be installed ---
that the integrated components can be moved into their final
configuration. A fourth major area is in the integration of the %detector 
\dwords{detmodule} with the necessary services provided by the conventional
facilities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Configuration Management}
\label{sec:fdsp-coord-integ-config}

The \dword{tc} engineering team will maintain
configuration data in the appropriate format for the management of the
detector configuration. The consortia are responsible for providing
engineering data for their subsystems to \dword{tc}. The
\dword{tc} engineering team will work with the \dword{lbnf} project team to
integrate the full detector data into the global \dword{lbnf}
configuration files. Appropriate thresholds for tracking and for
change control will be established.

For mechanical design aspects, the \dword{tc} engineering team
will maintain full \threed CAD models of the \dwords{detmodule}. Appropriate level
of detail will be specified for each type of model. Each consortium
will be responsible for providing CAD models of their detector
components to be integrated into overall models. The \dword{tc} engineering
team will work with the \dword{lbnf} project team to integrate the
full \dword{detmodule} models into a global \dword{lbnf} CAD model which will
include cryostats, cryogenics systems, and the conventional
facilities. These will include models using varying software
packages. The \dword{tc} engineering team will work directly with the
consortium Technical Leads and their supporting engineering teams to
resolve any detector component interference or interface issues with
other detector systems, detector infrastructure, and facility
infrastructure.

For electrical design aspects, the \dword{tc} engineering team will maintain
high-level interface documents that describe all aspects of required
electrical infrastructure and electrical connections. All consortia
must document power requirements and rack space
requirements. Consortia are responsible for defining any cabling that
bridges the design efforts of two or more consortia. This agreed-upon
and signed-off interface documentation shall include cable
specification, connector specification, connector pinout and any data
format, signal levels and timing. All cables, connectors, printed
circuit board components, physical layout and construction will be
subject to project review. This is especially true of elements which
will be inaccessible during the project lifetime. Consortia shall
provide details on \lar temperature acceptance testing and
lifetime of components, boards, cables and connectors.


At the time of the release of the \dword{tdr}, the
\dword{tc} engineering team will work with the consortia to produce
formal engineering drawings for all detector components.  These
drawings are expected to be signed by the consortia Technical Leads,
project engineers, and Technical Coordinator.  Starting from that
point, the \dwords{detmodule} models and drawings will sit under formal change
control as discussed in Section~\ref{sec:fdsp-coord-qa}.  It is
anticipated that designs will undergo further revisions prior to the
start of detector construction, but any changes made after the release
of the \dword{tdr} will need to be agreed to by all of
the drawing signers and an updated, signed drawing produced. The major
areas of configuration management include:
\begin{enumerate}
  \item \threed model,
  \item Interface definitions,
  \item Envelope drawings for installation,
  \item Drawing management.
\end{enumerate}

\Dword{tc} will put into place processes for configuration
management.  Configuration management will provide \dword{tc}
and engineering staff the ability to define and control
the actual build of the detector at any point in time and to track any
changes which may occur over duration of the build as well as the
lifetime of the project as described in
Section~\ref{sec:fdsp-coord-qa}.

For detector elements within a cryostat, configuration management
will be frozen once the elements are permanently sealed within the
cryostat.  However, during the integration and installation process of
building the \dwords{detmodule} within the cryostat, changes may need to occur.
For detector elements outside the cryostat and accessible, all
repairs, replacements, hardware upgrades, system grounding changes,
firmware and software changes must be tracked.

Any change will require revision control, configuration
identification, change management and release management.

{\bf Revision Control}\\ Consortia will be responsible for providing
accurate and well documented revision control.  Revision control
will provide a method of tracking and maintaining the history of
changes to a detector element.  Each detector element must be clearly
identified with a document which includes a revision number and
revision history.  For mechanical elements, this will be reflected by
a drawing number with revision information.  For electrical elements,
schematics will be used to track revisions.  Consortia will be
responsible for identifying the revision status of each installed
detector element. Revisions are further controlled through maintenance
of the documents in DocDB and \dword{edms}.

{\bf Configuration Identification}\\
Consortia are responsible for providing unique identifiers or part
numbers for each detector element.  Plans will be developed on how
inventories will be maintained and tracked during the build.  Plans
will clearly identify any dynamic configuration modes which may be
unique to a specific detector element.  For example, a printed circuit
board may have firmware that effects its performance.

{\bf Change Management}\\
\dword{tc} will provide guidelines
for formal change management.  During the beginning phase of the
project, drawings and interface documents are expected to be signed by
the consortium Technical Leads, project engineers, and Technical
Coordinator.  Once this initial design phase is complete, the detector
models, drawings, schematics and interface documents will be under
formal change control.  It is anticipated that designs will undergo
further revisions prior to the start of detector construction, but any
changes made after the release of the \dword{tdr} will
need to be agreed to by all drawing signers and an updated signed
drawing produced.

{\bf Release Management}\\
Release management focuses on the delivery of the more dynamic aspects
of the project such as firmware and software.  Consortia with
deliverables that have the potential to affect performance of the
detector by changing firmware or software must provide plans on how
these revisions will be tracked, tested and released.  The
modification of any software or firmware after the initial release,
must be formally controlled, agreed upon and tracked.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Engineering Process and Support}
\label{sec:fdsp-coord-integ-engr-proc}
 

The \dword{tc} organization will work with
the consortia through its \dword{tc} engineering team to ensure the proper
integration of all detector components.  The \dword{tc} engineering team will
document requirements on engineering standards and documentation that
the consortia will need to adhere to in the design process for the
detector components under their responsibility.  Similarly, the
project \dword{qa} and \dword{esh} managers will document \dword{qc} and safety
criteria that the consortia will be required to follow during the
construction, installation, and commissioning of their detector
components, as discussed in sections~\ref{sec:fdsp-coord-qa}
and~\ref{sec:fdsp-coord-esh}.


Consortia interfaces with the conventional facilities, cryostats, and
cryogenics are managed through the \dword{tc}
organization.  The \dword{tc} engineering team will work with the
consortia to understand their interfaces to the facilities and then
communicate these globally to the \dword{lbnf} Project team.  For conventional
facilities the types of interfaces to be considered are requirements
for bringing needed detector components down the shaft and through the
underground tunnels to the appropriate detector cavern, overall requirements for
power and cooling in the detector caverns, and the requirements on
cable connections from the underground area to the surface.
Interfaces to the cryostat include the number and sizes of the
penetrations on top of the cryostat, required mechanical structures
attaching to the cryostat walls for supporting cables and
instrumentation, and requirements on the global positioning of the
\dwords{detmodule} within the cryostat.  Cryogenics system interfaces include
requirements on the location of inlet and output ports, requirements on
the monitoring of the \lar both inside and outside the
cryostat, and grounding and shielding requirements on piping attached to
the cryostat.

\dword{lbnf} will be responsible for the design and construction of the
cryostats used to house the \dwords{detmodule}.  The consortia are required to
provide input on the location and sizes of the needed penetrations at
the top of the cryostats.  The consortia also need to specify any
mechanical structures to be attached to the cryostat walls for
supporting cables or instrumentation.  The \dword{tc} engineering
team will work with the \dword{lbnf} cryostat engineering team to understand
what attached fixturing is possible and iterate with the consortia as
necessary.  The consortia will also work with the \dword{tc} engineering
team through the development of the \threed CAD model to understand the
overall position of the \dwords{detmodule} within the cryostat and any issues
associated with the resulting locations of their detector components.

\dword{lbnf} will be responsible for the cryogenics systems used to purge,
cool, and fill the cryostats.  It will also be responsible for the
system that continually re-circulates \lar through filtering
systems to remove impurities.  Any detector requirements on the flow
of liquid within the cryostat %should \fixme{should? (also elsewhere in this file} 
will be developed by the consortia and
transmitted to \dword{lbnf} through the \dword{tc} engineering team.  Similarly,
any requirements on the rate of cool-down or maximum temperature
differential across the cryostat during the cool-down process will %should
be specified by the consortia and transmitted to the \dword{lbnf} team.

The engineering design process is defined by a set of steps taken to
fulfill the requirements of the design.  By the time of the \dword{tdr}, 
all design requirements must be fully defined and
proposed designs must be shown to meet these requirements.  Based on
prior work, some detector elements may be quite advanced in the
engineering process, while others may be in earlier stages.  Each
design process shall closely follow the engineering steps described
below.


{\bf Development of specifications}\\ Each consortium is responsible
for the technical review and approval of the engineering
specifications.  The documented specifications for all major design
elements will %should 
include the scope of work, project milestones,
relevant codes and standards to be followed, acceptance criteria and
specify appropriate internal or external design reviews.
Specifications shall be treated as controlled documents and cannot be
altered without approval of the \dword{tc}
team.  The \dword{tc} engineering team will participate in and help facilitate
all major reviews as described in
Section~\ref{sec:fdsp-coord-reviews}.  Special TB reviews
will be scheduled for major detector elements.

{\bf Engineering Risk Analysis}\\ Each consortium is responsible for
identifying and defining the level of risk associated with their
deliverables as described in Section~\ref{sec:fdsp-coord-risk}.
\Dword{tc} will work with the consortia,
through its \dword{tc} engineering team, to document these risks in a Risk
Database and follow them throughout the project until they are
realized or can be retired.

{\bf Specification Review}\\
The \dword{dune} \dword{tc} organization and project engineers
shall review consortium specifications for overall compliance with the
project requirements.  Consortia must document all internal reviews
and provide that documentation to \dword{tc}.
Additional higher-level reviews may be scheduled by \dword{tc}
as described in Section~\ref{sec:fdsp-coord-reviews}.

{\bf System Design}\\
The system design process includes the production of mechanical
drawings, electrical schematics, calculations which verify compliance
to engineering standards, firmware, printed circuit board layout,
cabling and connector specification, software plans, and any other
aspects that lead to a fully documented functional design.  All
relevant documentation shall be recorded, with appropriate document
number, into the chosen engineering data management system and be
available for the review process.

{\bf Design Review}\\ The design review process is determined by the
complexity and risk associated with the design element.  For a simple
design element, a consortium may do an internal review.  For a more
complex or high risk element a formal review will be scheduled.
\dword{dune} \dword{tc} will facilitate the review,
bringing in outside experts as needed.  In all cases, the result of
any reviews must be well documented and captured in the engineering
data management system.  If recommendations are made, those
recommendations will be tracked in a database and the consortia will
be expected to provide responses. All results of these engineering
reviews will be made available for the subsystem design reviews
described in Section~\ref{sec:fdsp-coord-reviews}.

{\bf Procurement}\\ The procurement process will include the
documented technical specifications for all procured materials and
parts.  All procurement technical documents are reviewed for
compliance to engineering standards and \dword{esh} concerns.
\dword{dune} \dword{tc} will assist the consortia in working with
their procurement staff as needed.

{\bf Production and assembly}\\ During the implementation phase of the project,
the consortia shall provide the Technical Coordinator with updates on
schedule.  A test plan will be fully developed which will allow for
verification that the initial requirements have been met. This is part of
the \dword{qa} plan that will be documented and followed as described
in Section ~\ref{sec:fdsp-coord-qa}.

{\bf Testing and Validation\\} The testing plan documented in the
above step will be followed and results will be well documented in
consultation with the \dword{qam}.  The Technical Coordinator and \dword{tc}
engineering team will be informed as to the results and whether the
design meets the specifications.  If not, a plan will be formulated to
address any shortcomings and presented to the Technical Coordinator.

{\bf Final Documentation\\} Final reports will be generated that
describe the as built equipment, lessons learned, safety reports,
installation procedures, testing results and operations procedures.
