\chapter{Technical Coordination}
\label{ch:fdsp-coord}

Construction of the \dword{dune} Detector requires careful technical
coordination due to its complexity. The technology for massive noble
liquid detectors has developed over the last \num{45} years and the first
large \dword{lartpc} was completed in
2010. While multiple \dwords{lartpc} have operated worldwide, the technology
is still relatively new and the scale up to \dword{dune} presents
challenges. However, the technology is well suited to massive neutrino
detectors with millimeter scale resolution on \SI{100}{m} scale detectors and
the technical challenges are surmountable.

[refer to images of \dword{dune}-\dword{sp} and \dword{dune}-\dword{dp}?]

The \dword{dune} collaboration consists of a large number of
institutions distributed throughout the world. They are supported by a
large number of funding sources and collaborate with a large number of
commercial partners. \dword{dune} has empowered several consortia
(currently nine) with the responsibility to secure funding to design,
fabricate, assemble, install, commission and operate the key
components of the \dword{dune} far detector.

\dword{dune} Technical Coordination, under the direction of the
\dword{dune} Technical Coordinator, has the responsibility to monitor
the technical aspects of the detector construction, to integrate the
detector and to deliver the common projects. Groups of institutes
within \dword{dune} form consortia that take complete responsibility
for construction of their system.

Given the horizontal nature of the consortia structure and the
extensive interdependencies between the systems, a significant
engineering organization is required to deliver \dword{dune} on
schedule and within specifications and funding constraints.

The \dword{dune} Technical Coordinator reports to the \dword{dune}
Spokespersons and the FNAL Director. The responsibilities of Technical
Coordination include:
\begin{itemize}
  \item management and delivery of all common projects
  \item review of all aspects of the project
  \item configuration control of all interface drawings and envelopes
  \item development and tracking of project schedule and milestones
  \item project work, product and assembly breakdown schedules
  \item project risk register
  \item \dword{dune} engineering and safety standards, including grounding \& shielding
  \item monitoring of all consortia
  \item installation of detectors at the near and far sites
  \item logistics for detector integration and installation at the near and far sites
  \item quality assurance and all QA related studies and documents
  \item ES\&H organization and all saftey related studies and documents
  \item recording and approving all project engineering information, including: documents, drawings and models
  \item survey of the detector
  \item primary interface to \dword{lbnf} for conventional facilities, cryostat and cryogenics
  \item primary interface to the Host Lab for infrastructure and operations support (\dword{lbnf}?)
\end {itemize}

An organizational chart outlining the \dword{dune} TC organization is shown in
Figure~\ref{fig:dune_orgchart}. The TC organization staffing will need
to grow as the project advances. Eventually TC will provide staffing
for teams underground at SURF, at integration facilities and at the
near site at FNAL.

\dword{dune} TC interacts with \dword{lbnf} though the \dword{lbnf}/\dword{dune} systems engineering
organization. TC provides the points of contact between the consortia
and \dword{lbnf}.

[Do we need to summarize all of the TC deliverables? perhaps here? or
  perhaps in Installation (where they all reside)? Jim has a high
  level, 5-line summary in 9.2.1.]

\input{far-detector-generic/chapter-fd-coordination/support}
\input{far-detector-generic/chapter-fd-coordination/integration}
\input{far-detector-generic/chapter-fd-coordination/installation-sp}

